SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Remove covered points
Add comments to SBML code

model = sbml.load("repressilator.sbml")
model = biomodels.load_model("BIOMD12")  # repressilator model
Simulator(model).solve(...)
```

Cool stuff
Interactive
Pandas
Generate from sbml?
Speed leveraging backends

# Conclusion

>>>>

model = sbml.load("repressilator.sbml")  # from existing SBML file
model = biomodels.load_model("BIOMD12")  # from BioModels
Simulator(model).solve(...)
```

## Other things

units -> Pint
interactive

# Discussion
